Figure for Weather Comparison

### 2025-08-28 Weather_com_figure_ABP.Rmd
Updated the script so each plot is seperate

```{r Figure}
# Make the figure and save it in the figures folder

# Rename the variable to fit in the labels
hum_names <- as_labeller(
     c(`Rain_Total_sum_cm` = "Daily Rain Toal cm", `AirTemp_C_Average` = "Daily Average Air Temp C",`WindSpeed_Average_m_s` = "Daily Averge Wind Speed m/s"))

# Make the plot here
ggplot(met_all_long, aes(x = ddate, y = obs, color = as.factor(Year)))+
  geom_point()+ # point or line?
  facet_grid(vars(variable), scales = "free", labeller = hum_names)+
  labs(color='Year') + 
  ylab("")+
  xlab("Date")+
  scale_x_date(date_breaks = "2 month", date_minor_breaks = "1 month",
             date_labels = "%B")+
  theme_bw(base_size = 15) #size of all the text in the figure.

 # can change dimensions as you see fit 
ggsave("figures/Met_com_2018_2023.png", width = 10, height = 8, dpi = 300, units = "in", device='png')
```

>>>>

```{r Figure}
# Make the figures on one panel and save it in the figures folder
# Just going to comment this out, but save it

# # Rename the variable to fit in the labels
# hum_names <- as_labeller(
#      c(`Rain_Total_sum_cm` = "Daily Rain Toal cm", `AirTemp_C_Average` = "Daily Average Air Temp C",`WindSpeed_Average_m_s` = "Daily Averge Wind Speed m/s"))
# 
# # Make the plot here
# ggplot(met_all_long, aes(x = ddate, y = obs, color = as.factor(Year)))+
#   geom_point()+ # point or line?
#   facet_grid(vars(variable), scales = "free", labeller = hum_names)+
#   labs(color='Year') + 
#   ylab("")+
#   xlab("Date")+
#   scale_x_date(date_breaks = "2 month", date_minor_breaks = "1 month",
#              date_labels = "%B")+
#   theme_bw(base_size = 15) #size of all the text in the figure. 
# 
# 
#  # can change dimensions as you see fit 
# ggsave("figures/Met_com_2018_2023.png", width = 10, height = 8, dpi = 300, units = "in", device='png')
```
```{r Function to Make Plots}

# Function to make the Plots

met_plot <- function(data= met_all_long,
                     VAR, 
                     y_lab){

a <- met_all_long%>%
  filter(variable == VAR)%>%
ggplot(., aes(x = ddate, y = obs, color = as.factor(Year)))+
  geom_point()+ 
  labs(color='Year') +
  ylab(y_lab)+
  xlab("Date")+
  scale_x_date(date_breaks = "2 month", date_minor_breaks = "1 month",
             date_labels = "%B")+
  theme_bw(base_size = 18) #size of all the text in the figure.

return(a)
}
```

```{r Temp Plot}
temp <- met_plot(VAR = "AirTemp_C_Average", y_lab = expression(""* ~degree*C))
temp

 # can change dimensions as you see fit
ggsave("figures/SI_Met_Comp/Temp_2018_2023.png", plot = temp,width = 10, height = 8, dpi = 300, units = "in", device='png')

```{r Wind speed}

wind <- met_plot(VAR = "WindSpeed_Average_m_s", y_lab = "m/s")
wind

 # can change dimensions as you see fit
ggsave("figures/SI_Met_Comp/Wind_2018_2023.png", plot = wind, width = 10, height = 8, dpi = 300, units = "in", device='png')

```
```{r Rain}
rain <- met_plot(VAR = "Rain_Total_sum_cm", y_lab = "centimeters")
rain

 # can change dimensions as you see fit
ggsave("figures/SI_Met_Comp/Rain_2018_2023.png", plot = rain, width = 10, height = 8, dpi = 300, units = "in", device='png')

```{r Violin plots}
# Playing with box plots

Atemp <- met_2018_23%>%
  mutate(Year = year(DateTime))%>%
  ggplot(., aes(x = Year, y = AirTemp_C_Average, group = Year, fill = as.factor(Year)))+
  geom_violin()+
  theme_bw()

Atemp

Wspeed <- met_2018_23%>%
  mutate(Year = year(DateTime))%>%
  ggplot(., aes(x = Year, y = WindSpeed_Average_m_s, group = Year, fill = as.factor(Year)))+
  geom_violin()+
  theme_bw()

Wspeed
